### 2019-02-26 docs/notebooks/results.Rmd
rewrite 'Summary' as 'Abstract', flesh out. Possibly too strong

## Summary
Convolutional neural networks (CNNs) represent the state of the art in image recognition. Many mechanisms proposed to improve the performance of neural networks have been given the name "attention" [@xuShowAttendTell2015]. This may be surpising to scientists studying the visual system, who typically describe attention as a result of the limitated resources available for processing sensory inputs. These scientists have developed behavioral tasks to investigate visual attention. Such tasks may provide an alternate way of benchmarking existing neural network architectures, comparing their output with human behavior, and measuring how proposed attentional mechanisms change the output of neural networks. Here we adapt a classic form of visual search task so it can be performed by neural networks. We measure the accuracy of two CNNs, AlexNet and VGG16, as they report whether a target is present among distractors. These architectures were chosen in part because they have been used in several studies that report similarities between activations in the hidden layers of the network and activity in the visual system of the brain when presented with the same visual stimuli. Surprisingly, we find that both networks show attention-like effects when performing the task.

>>>>

## Abstract
Convolutional neural networks (CNNs) provide cutting edge tools for computer vision tasks like image classifcation and scene segmentation. However, they suffer from known flas. Many mechanisms proposed to improve the performance of neural networks have been given the name "attention" [@xuShowAttendTell2015]. This may be surpising to scientists studying the visual system, who typically describe attention as a result of the limitated resources available for processing sensory inputs. Attention in the brain has been primarily investiaged using visual search tasks. These tasks provide an alternate way of benchmarking existing neural network architectures, comparing their output with human behavior, and measuring how proposed attentional mechanisms change the output of neural networks. We are pursuing these alternate benchmarks for attentional mechanisms in the course of investigations of continual learning algorithms. Here we adapt a classic form of visual search task so it can be performed by neural networks. We measure the accuracy of two CNNs, AlexNet and VGG16, as they report whether a target is present among distractors. These architectures were chosen in part because they have been used in several studies that report similarities between activations in the hidden layers of the network and activity in the visual system of the brain, when presented with the same visual stimuli. Surprisingly, we find that both networks show attention-like effects when performing the task. When the target resembles the distractors, then a network's accuracy drops as the number of distractors increases. We do not find that these results can be explained by known factors to affect CNNs, such as edge effects. While it might seem like a given that target-distractor similarity impairs accuracy, qualtiatively similar findings in studies of human subjects have been used to conclude that the brain requires serial processing mechanisms. Given that we know that CNNs process their inputs effectively in parallel, we can conclusively attribute the impaired accuracy here to target-distractor similarity. Therefore, we suggest that any mechanism which can be reformulated as a learned weighting processed in parallel is not categorically different from current CNNs, and is not likely to improve performance, since it will just produce the kind of attention effects we describe here.
